---
title: "American Crocodile Scute Mercury Analyses"
author: "Kylie"
date: "2026-09-02"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# ============================================================
# American Crocodile Scute Mercury Analyses
# ============================================================
#
# Analyses:
#   1. Hg concentration and body size (SVL)
#   2. Hatchling clutch and nest-site effects
#   3. Juvenile sex effects
#   4. Hatchling vs. juvenile Hg concentrations
#   5. Publication figures and summary outputs
#
# Multiple scute subsamples from the same crocodile are averaged
# to obtain one individual-level THg concentration before all
# biological analyses. Because scute material could not be
# homogenized, these are treated as spatial subsamples rather
# than scute subsamples of a homogenized sample.
# ============================================================


# ------------------------------------------------------------
# 1. PACKAGES
# ------------------------------------------------------------

```{r packages}
library(readxl)
library(dplyr)
library(ggplot2)
library(lme4)
library(lmerTest)
library(emmeans)
library(performance)
library(patchwork)
library(forcats)
library(clubSandwich)
library(here)
library(see)
```

# ------------------------------------------------------------
# 2. IMPORT AND PREPARE DATA
# ------------------------------------------------------------

Multiple scute subsamples from the same crocodile were averaged to obtain
one individual-level THg concentration. Because scute material could not
be homogenized, these measurements were treated as spatial subsamples
rather than technical replicates of a homogenized sample.

## Import Raw Data

```{r import-data}
raw <- read_xlsx(
  here("American_Crocodile_Mercury_Data.xlsx")
)
```


# ------------------------------------------------------------
# Summarize scute subsamples within each crocodile
# ------------------------------------------------------------
#
# Scute material could not be homogenized before analysis.
# Repeated measurements from the same crocodile are therefore
# treated as spatial scute subsamples rather than conventional
# scute subsamples of a homogeneous tissue sample.
#
# The mean across available scute subsamples is used as the
# individual-level THg concentration for the PRIMARY analyses.
# Within-individual CV is calculated for quality assessment and
# for a separate sensitivity analysis using a 15% cutoff.
# ------------------------------------------------------------

```{r prepare-individual-data}
dat <- raw %>%
  group_by(`Scute ID`) %>%
  summarise(
    n_subsamples = sum(!is.na(`CONC [ug/kg]`)),
    Hg_ugkg = mean(`CONC [ug/kg]`, na.rm = TRUE),
    SD_Hg_ugkg = ifelse(
      n_subsamples > 1,
      sd(`CONC [ug/kg]`, na.rm = TRUE),
      NA_real_
    ),
    CV_percent = ifelse(
      n_subsamples > 1,
      (SD_Hg_ugkg / Hg_ugkg) * 100,
      NA_real_
    ),
    TL = first(`TL (cm)`),
    SizeClass = first(`Size Class`),
    SVL = first(`SVL (cm)`),
    Weight = first(`Weight (g)`),
    Sex = first(Sex),
    Clutch = first(Clutch),
    Site = first(`Nest Location`),
    .groups = "drop"
  ) %>%
  mutate(
     # Convert µg/kg to µg/g
    Hg_ugg = Hg_ugkg / 1000,
    SD_Hg_ugg = SD_Hg_ugkg / 1000,

    # Sensitivity-analysis flag.
    # Animals represented by one scute subsample are retained
    # because within-individual CV cannot be calculated.
    CV15_status = case_when(
      n_subsamples == 1 ~ "Single subsample - retained",
      CV_percent <= 15 ~ "CV <=15% - retained",
      CV_percent > 15 ~ "CV >15% - excluded in sensitivity analysis",
      TRUE ~ NA_character_
    ),
    CV15_include = n_subsamples == 1 | CV_percent <= 15,

    SizeClass = factor(
      SizeClass,
      levels = c("Hatchling", "Juvenile", "Subadult")
    ),

    Sex = factor(Sex),
    Clutch_f = factor(Clutch),
    Site = factor(Site),

    # Transformations used in statistical models
    logHg = log10(Hg_ugg),
    logSVL = log10(SVL)
  )
```

# Inspect within-individual scute variability

```{r within-individual-scute-variability}
dat %>%
  select(
    `Scute ID`, SizeClass, n_subsamples,
    Hg_ugg, SD_Hg_ugg, CV_percent, CV15_status
  ) %>%
  arrange(desc(CV_percent))
```

# Number retained/excluded by age class

```{r retained-or-excluded-by-age-class}
CV15_sample_summary <- dat %>%
  count(SizeClass, CV15_status, name = "n_individuals") %>%
  arrange(SizeClass, CV15_status)

CV15_sample_summary
```

# Individuals with >15% CV

```{r samples-CV-greater-than-15%}
CV15_excluded_individuals <- dat %>%
  filter(n_subsamples > 1, CV_percent > 15) %>%
  select(
    `Scute ID`, SizeClass, Sex, Clutch, Site,
    n_subsamples, Hg_ugg, SD_Hg_ugg, CV_percent
  ) %>%
  arrange(SizeClass, desc(CV_percent))

CV15_excluded_individuals
```

# Age-class datasets

```{r age-class-datasets}
hatchlings <- dat %>%
  filter(SizeClass == "Hatchling") %>%
  mutate(
    logSVL_c = logSVL - mean(logSVL, na.rm = TRUE)
  )

juveniles <- dat %>%
  filter(SizeClass == "Juvenile") %>%
  mutate(
    Sex = factor(Sex, levels = c("F", "M")),
    logSVL_c = logSVL - mean(logSVL, na.rm = TRUE)
  )
```

# Confirm sample sizes

```{r confirm-sample-sizes}
table(dat$SizeClass)
table(juveniles$Sex)
```

# ============================================================
# ANALYSIS 1. BODY SIZE AND SCUTE Hg
# ============================================================

# ------------------------------------------------------------
# 1A. All individuals
# ------------------------------------------------------------

# Analysis 1. Body Size and Scute THg

## 1A. All Individuals

```{r body-size-all}
mod_SVL_all <- lm(
  logHg ~ logSVL,
  data = dat
)

summary(mod_SVL_all)
confint(mod_SVL_all)
performance::r2(mod_SVL_all)
performance::check_model(mod_SVL_all)
```


## 1B. Juveniles

```{r body-size-juveniles}
mod_SVL_juvenile <- lm(
  logHg ~ logSVL,
  data = juveniles
)

summary(mod_SVL_juvenile)
confint(mod_SVL_juvenile)
performance::r2(mod_SVL_juvenile)
performance::check_model(mod_SVL_juvenile)
```

## 1C. Hatchlings

```{r body-size-hatchlings}
mod_SVL_hatchling <- lmer(
  logHg ~ logSVL_c + (1 | Clutch_f),
  data = hatchlings,
  REML = TRUE
)

summary(mod_SVL_hatchling)
anova(mod_SVL_hatchling)
confint(mod_SVL_hatchling, method = "Wald")
performance::r2(mod_SVL_hatchling)
performance::check_model(mod_SVL_hatchling)
```

# Fixed-effect predictions for hatchling figure

```{r fixed-effects-hatchlings}
SVL_seq <- seq(
  min(hatchlings$logSVL_c, na.rm = TRUE),
  max(hatchlings$logSVL_c, na.rm = TRUE),
  length.out = 200
)

pred_hatch <- emmeans(
  mod_SVL_hatchling,
  ~ logSVL_c,
  at = list(logSVL_c = SVL_seq)
) %>%
  as.data.frame()

pred_hatch$logSVL <- pred_hatch$logSVL_c +
  mean(hatchlings$logSVL, na.rm = TRUE)
```

# ============================================================
# ANALYSIS 2. HATCHLING CLUTCH AND NEST-SITE EFFECTS
# ============================================================


# ------------------------------------------------------------
# 2A. Sample structure
# ------------------------------------------------------------

```{r clutch-structure}
clutch_structure <- hatchlings %>%
  count(Site, Clutch_f, name = "n_hatchlings") %>%
  arrange(Site, Clutch_f)

clutch_structure
```

# ------------------------------------------------------------
# 2B. Variance attributable to clutch
# ------------------------------------------------------------

```{r clutch-variance}
mod_clutch <- lmer(
  logHg ~ 1 + (1 | Clutch_f),
  data = hatchlings,
  REML = TRUE
)

summary(mod_clutch)

icc_clutch <- performance::icc(
  mod_clutch,
  ci = 0.95
)

icc_clutch
```

# ------------------------------------------------------------
# 2C. Nest-site effect accounting for clutch
# ------------------------------------------------------------

```{r nest-site-effect}
mod_site_clutch <- lmer(
  logHg ~ Site + (1 | Clutch_f),
  data = hatchlings,
  REML = TRUE
)

summary(mod_site_clutch)
anova(mod_site_clutch)
performance::r2(mod_site_clutch)
performance::icc(mod_site_clutch, ci = 0.95)
performance::check_singularity(mod_site_clutch)
performance::check_model(mod_site_clutch)
```

# Estimated marginal means by site

```{r EMM-by-site}
site_emm <- emmeans(
  mod_site_clutch,
  ~ Site
)

site_emm
pairs(site_emm, adjust = "tukey")

site_results <- as.data.frame(
  confint(site_emm)
) %>%
  mutate(
    Hg_ugg = 10^emmean,
    lower_Hg = 10^lower.CL,
    upper_Hg = 10^upper.CL
  )

site_results
```

# ============================================================
# ANALYSIS 3. JUVENILE SEX EFFECTS
# ============================================================


# ------------------------------------------------------------
# 3A. Does body size differ by sex?
# ------------------------------------------------------------

```{r juvenile-sex-effect}
juvenile_sex_summary <- juveniles %>%
  group_by(Sex) %>%
  summarise(
    n = n(),
    mean_SVL = mean(SVL, na.rm = TRUE),
    SD_SVL = sd(SVL, na.rm = TRUE),
    median_SVL = median(SVL, na.rm = TRUE),
    min_SVL = min(SVL, na.rm = TRUE),
    max_SVL = max(SVL, na.rm = TRUE),
    .groups = "drop"
  )

juvenile_sex_summary

sex_SVL_test <- t.test(
  SVL ~ Sex,
  data = juveniles
)

sex_SVL_test
```

# ------------------------------------------------------------
# 3B. Does the Hg-SVL relationship differ by sex?
# ------------------------------------------------------------

```{r Hg-SVL-Sex}
mod_sex_interaction <- lm(
  logHg ~ logSVL_c * Sex,
  data = juveniles
)

summary(mod_sex_interaction)
anova(mod_sex_interaction)

sex_slopes <- emtrends(
  mod_sex_interaction,
  ~ Sex,
  var = "logSVL_c"
)

sex_slopes
pairs(sex_slopes)
```

# ------------------------------------------------------------
# 3C. Does sex predict Hg after accounting for SVL?
# ------------------------------------------------------------

```{r sex-adjusted-model}
mod_sex_adjusted <- lm(
  logHg ~ logSVL_c + Sex,
  data = juveniles
)

summary(mod_sex_adjusted)
anova(mod_sex_adjusted)
confint(mod_sex_adjusted)
performance::r2(mod_sex_adjusted)
performance::check_model(mod_sex_adjusted)

performance::check_collinearity(mod_sex_adjusted)
```

# Adjusted Hg estimates at mean juvenile body size

```{r EMM-Ses}
sex_emm <- emmeans(
  mod_sex_adjusted,
  ~ Sex
)

sex_results <- as.data.frame(
  confint(sex_emm)
) %>%
  mutate(
    Hg_ugg = 10^emmean,
    lower_Hg = 10^lower.CL,
    upper_Hg = 10^upper.CL
  )

sex_results
pairs(sex_emm)
```

# Compare SVL-only model with SVL + sex model

```{r model-comparison}
mod_SVL_only <- lm(
  logHg ~ logSVL_c,
  data = juveniles
)

anova(
  mod_SVL_only,
  mod_sex_adjusted
)
```

# ============================================================
# ANALYSIS 4. HATCHLING VS. JUVENILE Hg
# ============================================================

# Subadult excluded from this two-group comparison

```{r subadult-removed}
sizeclass_dat <- dat %>%
  filter(SizeClass %in% c("Hatchling", "Juvenile")) %>%
  droplevels()
```

# ------------------------------------------------------------
# 4A. Descriptive statistics
# ------------------------------------------------------------

```{r size-class-summary}
sizeclass_summary <- sizeclass_dat %>%
  group_by(SizeClass) %>%
  summarise(
    n = n(),
    mean_Hg = mean(Hg_ugg, na.rm = TRUE),
    SD_Hg = sd(Hg_ugg, na.rm = TRUE),
    median_Hg = median(Hg_ugg, na.rm = TRUE),
    min_Hg = min(Hg_ugg, na.rm = TRUE),
    max_Hg = max(Hg_ugg, na.rm = TRUE),
    .groups = "drop"
  )

sizeclass_summary
```

# ------------------------------------------------------------
# 4B. Welch's t-test on log-transformed Hg
# ------------------------------------------------------------

```{r size-class-welchs}
sizeclass_test <- t.test(
  logHg ~ SizeClass,
  data = sizeclass_dat
)

sizeclass_test
```

# ------------------------------------------------------------
# 4C. Geometric means and group-specific 95% CI
# ------------------------------------------------------------

```{r size-class-GeoMean}
sizeclass_geo <- sizeclass_dat %>%
  group_by(SizeClass) %>%
  summarise(
    n = n(),
    mean_log = mean(logHg, na.rm = TRUE),
    sd_log = sd(logHg, na.rm = TRUE),
    SE_log = sd_log / sqrt(n),
    tcrit = qt(0.975, df = n - 1),
    
    geometric_mean = 10^mean_log,
    
    lower_CI = 10^(mean_log - tcrit * SE_log),
    upper_CI = 10^(mean_log + tcrit * SE_log),
    
    .groups = "drop"
  )

sizeclass_geo
```

# Juvenile:Hatchling geometric-mean ratio
# Welch output is Hatchling - Juvenile, so signs are reversed.

```{r size-class-log-ratio}
log_ratio <- -diff(sizeclass_test$estimate)
```

# Difference in geometric means on the log10 scale

```{r size-class-log-difference}
log_difference <- (
  mean(sizeclass_dat$logHg[sizeclass_dat$SizeClass == "Juvenile"]) -
    mean(sizeclass_dat$logHg[sizeclass_dat$SizeClass == "Hatchling"])
)
```

# Back-transform to obtain juvenile:hatchling ratio

```{r size-class-fold-difference}
fold_difference <- 10^log_difference

fold_difference

fold_CI <- 10^c(
  -sizeclass_test$conf.int[2],
  -sizeclass_test$conf.int[1]
)

cat(
  "\nJuvenile:Hatchling geometric mean ratio =",
  round(fold_difference, 2),
  "\n95% CI =",
  round(fold_CI[1], 2), "to",
  round(fold_CI[2], 2),
  "\n"
)
```

# ============================================================
# ANALYSIS 4D. CLUSTER-AWARE HATCHLING VS. JUVENILE COMPARISON
# ============================================================
#
# Hatchlings from the same clutch are not fully independent.
# This analysis uses CR2 cluster-robust standard errors, with
# clutch defining the cluster for hatchlings and each juvenile
# treated as an independent cluster.
#
# Requires: clubSandwich (loaded with other packages above)
# ============================================================


# ------------------------------------------------------------
# Create cluster IDs
# ------------------------------------------------------------

```{r create-cluster-IDs}
sizeclass_cluster <- sizeclass_dat %>%
  mutate(
    cluster_id = if_else(
      SizeClass == "Hatchling",
      paste0("H_", Clutch),
      paste0("J_", `Scute ID`)
    )
  )
```

# Check cluster structure

```{r size-class-cluster}
sizeclass_cluster %>%
  count(SizeClass, cluster_id)
```

# ------------------------------------------------------------
# Fit size-class model
# ------------------------------------------------------------

```{r fit-size-class-model}
mod_sizeclass_cluster <- lm(
  logHg ~ SizeClass,
  data = sizeclass_cluster
)
```

# ------------------------------------------------------------
# CR2 cluster-robust inference
# ------------------------------------------------------------

```{r cluster-test}
cluster_test <- coef_test(
  mod_sizeclass_cluster,
  vcov = "CR2",
  cluster = sizeclass_cluster$cluster_id,
  test = "Satterthwaite"
)

cluster_test
```

# Cluster-robust 95% confidence intervals

```{r cluster-confidence-intervals}
cluster_CI <- conf_int(
  mod_sizeclass_cluster,
  vcov = "CR2",
  cluster = sizeclass_cluster$cluster_id,
  test = "Satterthwaite"
)

cluster_CI
```

# ------------------------------------------------------------
# Back-transform juvenile:hatchling effect
# ------------------------------------------------------------

# Hatchling is the reference group, so the Juvenile coefficient
# represents log10(Juvenile Hg) - log10(Hatchling Hg).

```{r}
beta_stage <- coef(
  mod_sizeclass_cluster
)["SizeClassJuvenile"]

fold_cluster <- 10^beta_stage

fold_cluster
```

# ============================================================
# ANALYSIS 4E. CLUTCH-LEVEL SENSITIVITY ANALYSIS
# Compare hatchling clutch means with juvenile individuals
# ============================================================
#
# This provides a simple complementary analysis in which each
# hatchling clutch contributes one independent observation.
# ============================================================

```{r clutch-sensitivity-analysis}
hatch_clutch_means <- hatchlings %>%
  group_by(Clutch_f) %>%
  summarise(
    logHg = mean(logHg, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  mutate(
    SizeClass = "Hatchling"
  )

juvenile_individuals <- juveniles %>%
  transmute(
    logHg,
    SizeClass = "Juvenile"
  )

sizeclass_sensitivity <- bind_rows(
  hatch_clutch_means,
  juvenile_individuals
) %>%
  mutate(
    SizeClass = factor(
      SizeClass,
      levels = c("Hatchling", "Juvenile")
    )
  )

sizeclass_sensitivity_test <- t.test(
  logHg ~ SizeClass,
  data = sizeclass_sensitivity
)

sizeclass_sensitivity_test
```

# ============================================================
# ANALYSIS 5. SENSITIVITY ANALYSIS USING WITHIN-INDIVIDUAL
# SCUTE-SUBSAMPLE CV <= 15%
# ============================================================
#
# PURPOSE:
# Determine whether the primary biological conclusions change
# when individuals with >15% variability among multiple scute
# subsamples are excluded.
#
# IMPORTANT:
# - This does NOT replace the primary analysis.
# - Animals represented by one scute subsample are retained,
#   because a within-individual CV cannot be calculated.
# - Centering and derived datasets are recreated after filtering.
# ============================================================


# ------------------------------------------------------------
# 5A. Create CV-restricted individual-level dataset
# ------------------------------------------------------------

```{r CV-restricted-dataset}
dat_CV15 <- dat %>%
  filter(CV15_include) %>%
  droplevels()

hatchlings_CV15 <- dat_CV15 %>%
  filter(SizeClass == "Hatchling") %>%
  mutate(
    Clutch_f = factor(Clutch),
    Site = factor(Site),
    logSVL_c = logSVL - mean(logSVL, na.rm = TRUE)
  )

juveniles_CV15 <- dat_CV15 %>%
  filter(SizeClass == "Juvenile") %>%
  mutate(
    Sex = factor(Sex, levels = c("F", "M")),
    logSVL_c = logSVL - mean(logSVL, na.rm = TRUE)
  )

CV15_n_comparison <- bind_rows(
  dat %>%
    count(SizeClass, name = "n") %>%
    mutate(dataset = "Primary - all individuals"),
  dat_CV15 %>%
    count(SizeClass, name = "n") %>%
    mutate(dataset = "Sensitivity - CV <=15% or single subsample")
) %>%
  select(dataset, SizeClass, n)

CV15_n_comparison
```

# ------------------------------------------------------------
# 5B. Body size and THg: all individuals
# ------------------------------------------------------------

```{r body-size-all-restricted}
mod_SVL_all_CV15 <- lm(
  logHg ~ logSVL,
  data = dat_CV15
)

summary(mod_SVL_all_CV15)
confint(mod_SVL_all_CV15)
performance::r2(mod_SVL_all_CV15)
```

# ------------------------------------------------------------
# 5C. Body size and THg: juveniles
# ------------------------------------------------------------

```{r body-size-juveniles-restricted}
mod_SVL_juvenile_CV15 <- lm(
  logHg ~ logSVL,
  data = juveniles_CV15
)

summary(mod_SVL_juvenile_CV15)
confint(mod_SVL_juvenile_CV15)
performance::r2(mod_SVL_juvenile_CV15)
```

# ------------------------------------------------------------
# 5D. Body size and THg: hatchlings, accounting for clutch
# ------------------------------------------------------------

```{r body-size-clutch-restricted}
mod_SVL_hatchling_CV15 <- lmer(
  logHg ~ logSVL_c + (1 | Clutch_f),
  data = hatchlings_CV15,
  REML = TRUE
)

summary(mod_SVL_hatchling_CV15)
anova(mod_SVL_hatchling_CV15)
confint(mod_SVL_hatchling_CV15, method = "Wald")
performance::r2(mod_SVL_hatchling_CV15)
```

# ------------------------------------------------------------
# 5E. Hatchling clutch ICC
# ------------------------------------------------------------

```{r clutch-ICC-restricted}
mod_clutch_CV15 <- lmer(
  logHg ~ 1 + (1 | Clutch_f),
  data = hatchlings_CV15,
  REML = TRUE
)

summary(mod_clutch_CV15)

icc_clutch_CV15 <- performance::icc(
  mod_clutch_CV15,
  ci = 0.95
)

icc_clutch_CV15
```

# ------------------------------------------------------------
# 5F. Hatchling nest-site effect accounting for clutch
# ------------------------------------------------------------

```{r nest-site-effect-clutch-restricted}
mod_site_clutch_CV15 <- lmer(
  logHg ~ Site + (1 | Clutch_f),
  data = hatchlings_CV15,
  REML = TRUE
)

summary(mod_site_clutch_CV15)
anova(mod_site_clutch_CV15)
performance::r2(mod_site_clutch_CV15)
performance::icc(mod_site_clutch_CV15, ci = 0.95)
performance::check_singularity(mod_site_clutch_CV15)

site_emm_CV15 <- emmeans(
  mod_site_clutch_CV15,
  ~ Site
)

site_emm_CV15
pairs(site_emm_CV15, adjust = "tukey")
```

# ------------------------------------------------------------
# 5G. Juvenile sex effects
# ------------------------------------------------------------

```{r juvenile-sex-effects-restricted}
juvenile_sex_summary_CV15 <- juveniles_CV15 %>%
  group_by(Sex) %>%
  summarise(
    n = n(),
    mean_SVL = mean(SVL, na.rm = TRUE),
    SD_SVL = sd(SVL, na.rm = TRUE),
    median_SVL = median(SVL, na.rm = TRUE),
    min_SVL = min(SVL, na.rm = TRUE),
    max_SVL = max(SVL, na.rm = TRUE),
    .groups = "drop"
  )

juvenile_sex_summary_CV15

sex_SVL_test_CV15 <- t.test(
  SVL ~ Sex,
  data = juveniles_CV15
)

sex_SVL_test_CV15

mod_sex_interaction_CV15 <- lm(
  logHg ~ logSVL_c * Sex,
  data = juveniles_CV15
)

summary(mod_sex_interaction_CV15)
anova(mod_sex_interaction_CV15)

sex_slopes_CV15 <- emtrends(
  mod_sex_interaction_CV15,
  ~ Sex,
  var = "logSVL_c"
)

sex_slopes_CV15
pairs(sex_slopes_CV15)

mod_sex_adjusted_CV15 <- lm(
  logHg ~ logSVL_c + Sex,
  data = juveniles_CV15
)

summary(mod_sex_adjusted_CV15)
anova(mod_sex_adjusted_CV15)
confint(mod_sex_adjusted_CV15)
performance::r2(mod_sex_adjusted_CV15)

sex_emm_CV15 <- emmeans(
  mod_sex_adjusted_CV15,
  ~ Sex
)

sex_emm_CV15
pairs(sex_emm_CV15)

```

# ------------------------------------------------------------
# 5H. Hatchling vs juvenile age-class comparison:
# CR2 cluster-robust inference
# ------------------------------------------------------------

```{r age-class-comparison-restricted}
sizeclass_CV15 <- dat_CV15 %>%
  filter(SizeClass %in% c("Hatchling", "Juvenile")) %>%
  droplevels() %>%
  mutate(
    SizeClass = factor(
      SizeClass,
      levels = c("Hatchling", "Juvenile")
    ),
    cluster_id = if_else(
      SizeClass == "Hatchling",
      paste0("H_", Clutch),
      paste0("J_", `Scute ID`)
    )
  )

mod_sizeclass_cluster_CV15 <- lm(
  logHg ~ SizeClass,
  data = sizeclass_CV15
)

cluster_test_CV15 <- coef_test(
  mod_sizeclass_cluster_CV15,
  vcov = "CR2",
  cluster = sizeclass_CV15$cluster_id,
  test = "Satterthwaite"
)

cluster_test_CV15

cluster_CI_CV15 <- conf_int(
  mod_sizeclass_cluster_CV15,
  vcov = "CR2",
  cluster = sizeclass_CV15$cluster_id,
  test = "Satterthwaite"
)

cluster_CI_CV15

beta_stage_CV15 <- coef(
  mod_sizeclass_cluster_CV15
)["SizeClassJuvenile"]

fold_cluster_CV15 <- 10^beta_stage_CV15

fold_cluster_CV15

```

# ------------------------------------------------------------
# 5I. Clutch-mean sensitivity within CV-restricted dataset
# ------------------------------------------------------------

```{r clutch-mean-sensitivity-restricted}
hatch_clutch_means_CV15 <- hatchlings_CV15 %>%
  group_by(Clutch_f) %>%
  summarise(
    logHg = mean(logHg, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  mutate(
    SizeClass = "Hatchling"
  )

juvenile_individuals_CV15 <- juveniles_CV15 %>%
  transmute(
    logHg,
    SizeClass = "Juvenile"
  )

sizeclass_clutchmean_CV15 <- bind_rows(
  hatch_clutch_means_CV15,
  juvenile_individuals_CV15
) %>%
  mutate(
    SizeClass = factor(
      SizeClass,
      levels = c("Hatchling", "Juvenile")
    )
  )

sizeclass_clutchmean_test_CV15 <- t.test(
  logHg ~ SizeClass,
  data = sizeclass_clutchmean_CV15
)

sizeclass_clutchmean_test_CV15
```

# ------------------------------------------------------------
# 5J. Compact primary vs CV15 model summary
# ------------------------------------------------------------

```{r primary-vs-restricted-model-summary}
CV15_model_summary <- bind_rows(

  data.frame(
    Analysis = "All animals: THg ~ SVL",
    Dataset = "Primary",
    N = nobs(mod_SVL_all),
    Estimate = coef(mod_SVL_all)["logSVL"],
    P_value = coef(summary(mod_SVL_all))["logSVL", "Pr(>|t|)"],
    R2 = summary(mod_SVL_all)$r.squared
  ),

  data.frame(
    Analysis = "All animals: THg ~ SVL",
    Dataset = "CV15 sensitivity",
    N = nobs(mod_SVL_all_CV15),
    Estimate = coef(mod_SVL_all_CV15)["logSVL"],
    P_value = coef(summary(mod_SVL_all_CV15))["logSVL", "Pr(>|t|)"],
    R2 = summary(mod_SVL_all_CV15)$r.squared
  ),

  data.frame(
    Analysis = "Juveniles: THg ~ SVL",
    Dataset = "Primary",
    N = nobs(mod_SVL_juvenile),
    Estimate = coef(mod_SVL_juvenile)["logSVL"],
    P_value = coef(summary(mod_SVL_juvenile))["logSVL", "Pr(>|t|)"],
    R2 = summary(mod_SVL_juvenile)$r.squared
  ),

  data.frame(
    Analysis = "Juveniles: THg ~ SVL",
    Dataset = "CV15 sensitivity",
    N = nobs(mod_SVL_juvenile_CV15),
    Estimate = coef(mod_SVL_juvenile_CV15)["logSVL"],
    P_value = coef(summary(mod_SVL_juvenile_CV15))["logSVL", "Pr(>|t|)"],
    R2 = summary(mod_SVL_juvenile_CV15)$r.squared
  ),

  data.frame(
    Analysis = "Hatchlings: THg ~ SVL + clutch",
    Dataset = "Primary",
    N = nobs(mod_SVL_hatchling),
    Estimate = fixef(mod_SVL_hatchling)["logSVL_c"],
    P_value = anova(mod_SVL_hatchling)["logSVL_c", "Pr(>F)"],
    R2 = performance::r2(mod_SVL_hatchling)$R2_marginal
  ),

  data.frame(
    Analysis = "Hatchlings: THg ~ SVL + clutch",
    Dataset = "CV15 sensitivity",
    N = nobs(mod_SVL_hatchling_CV15),
    Estimate = fixef(mod_SVL_hatchling_CV15)["logSVL_c"],
    P_value = anova(mod_SVL_hatchling_CV15)["logSVL_c", "Pr(>F)"],
    R2 = performance::r2(mod_SVL_hatchling_CV15)$R2_marginal
  ),

  data.frame(
    Analysis = "Juveniles: sex adjusted for SVL",
    Dataset = "Primary",
    N = nobs(mod_sex_adjusted),
    Estimate = coef(mod_sex_adjusted)["SexM"],
    P_value = coef(summary(mod_sex_adjusted))["SexM", "Pr(>|t|)"],
    R2 = summary(mod_sex_adjusted)$r.squared
  ),

  data.frame(
    Analysis = "Juveniles: sex adjusted for SVL",
    Dataset = "CV15 sensitivity",
    N = nobs(mod_sex_adjusted_CV15),
    Estimate = coef(mod_sex_adjusted_CV15)["SexM"],
    P_value = coef(summary(mod_sex_adjusted_CV15))["SexM", "Pr(>|t|)"],
    R2 = summary(mod_sex_adjusted_CV15)$r.squared
  )
)

CV15_model_summary

cat(
  "\nPRIMARY juvenile:hatchling CR2 fold difference =",
  round(fold_cluster, 2),
  "\nCV15 juvenile:hatchling CR2 fold difference =",
  round(fold_cluster_CV15, 2),
  "\n"
)

cat("\nPRIMARY hatchling clutch ICC:\n")
print(icc_clutch)

cat("\nCV15 hatchling clutch ICC:\n")
print(icc_clutch_CV15)

cat("\nPRIMARY nest-site omnibus test:\n")
print(anova(mod_site_clutch))

cat("\nCV15 nest-site omnibus test:\n")
print(anova(mod_site_clutch_CV15))

```

# ============================================================
# 6. FIGURES
# ============================================================


# ============================================================
# FIGURE 2. BODY SIZE AND SIZE-CLASS PATTERNS
# ============================================================


# ------------------------------------------------------------
# Statistical labels
# ------------------------------------------------------------

```{r summary-SVL-all}
sum_all <- summary(mod_SVL_all)

label_all <- paste0(
  "R² = ", sprintf("%.3f", sum_all$r.squared), "\n",
  ifelse(
    coef(sum_all)["logSVL", "Pr(>|t|)"] < 0.0001,
    "p < 0.0001",
    paste0(
      "p = ",
      sprintf("%.3f", coef(sum_all)["logSVL", "Pr(>|t|)"])
    )
  )
)


sum_juv <- summary(mod_SVL_juvenile)

label_juv <- paste0(
  "R² = ", sprintf("%.3f", sum_juv$r.squared), "\n",
  ifelse(
    coef(sum_juv)["logSVL", "Pr(>|t|)"] < 0.0001,
    "p < 0.0001",
    paste0(
      "p = ",
      sprintf("%.3f", coef(sum_juv)["logSVL", "Pr(>|t|)"])
    )
  )
)


R2_hatch <- performance::r2(
  mod_SVL_hatchling
)$R2_marginal

p_hatch <- anova(
  mod_SVL_hatchling
)["logSVL_c", "Pr(>F)"]

label_hatch <- paste0(
  "Marginal R² = ", sprintf("%.3f", R2_hatch), "\n",
  "p = ", sprintf("%.3f", p_hatch)
)
```

# ------------------------------------------------------------
# Colors for age class
# ------------------------------------------------------------

```{r age-class-colors}
age_colors <- c(
  "Hatchling" = "#56B4E9",
  "Juvenile"  = "#D55E00"
)
```

# ------------------------------------------------------------
# Panel A: All individuals
# ------------------------------------------------------------

```{r Figure-2-Panel-A}
pA <- ggplot(
  dat,
  aes(logSVL, logHg)
) +
  geom_point(
    size = 2.3,
    alpha = 0.75
  ) +
  geom_smooth(
    method = "lm",
    formula = y ~ x,
    se = TRUE,
    linewidth = 0.9
  ) +
  annotate(
    "text",
    x = -Inf,
    y = Inf,
    label = label_all,
    hjust = -0.12,
    vjust = 1.25,
    size = 4
  ) +
  labs(
    title = "THg by Body Size in All Animals",
    x = expression(Log[10]~"SVL (cm)"),
    y = expression(Log[10]~"scute THg (" * mu * "g/g)")
  ) +
  theme_classic(base_size = 12)
```

# ------------------------------------------------------------
# Panel B: Juveniles
# ------------------------------------------------------------

```{r Figure-2-Panel-B}
pB <- ggplot(
  juveniles,
  aes(logSVL, logHg)
) +
  geom_point(
    size = 2.3,
    alpha = 0.75
  ) +
  geom_smooth(
    method = "lm",
    formula = y ~ x,
    se = TRUE,
    linewidth = 0.9
  ) +
  annotate(
    "text",
    x = -Inf,
    y = Inf,
    label = label_juv,
    hjust = -0.12,
    vjust = 1.25,
    size = 4
  ) +
  labs(
    title = "THg by Body Size in Juveniles",
    x = expression(Log[10]~"SVL (cm)"),
    y = expression(Log[10]~"scute THg (" * mu * "g/g)")
  ) +
  theme_classic(base_size = 12)
```

# ------------------------------------------------------------
# Panel C: Hatchlings
# ------------------------------------------------------------

```{r Figure-2-Panel-C}
pC <- ggplot(
  hatchlings,
  aes(logSVL, logHg)
) +
  geom_point(
    size = 2.3,
    alpha = 0.75
  ) +
  geom_ribbon(
    data = pred_hatch,
    aes(
      x = logSVL,
      ymin = lower.CL,
      ymax = upper.CL
    ),
    inherit.aes = FALSE,
    alpha = 0.20
  ) +
  geom_line(
    data = pred_hatch,
    aes(
      x = logSVL,
      y = emmean
    ),
    inherit.aes = FALSE,
    linewidth = 0.9
  ) +
  annotate(
    "text",
    x = -Inf,
    y = Inf,
    label = label_hatch,
    hjust = -0.12,
    vjust = 1.25,
    size = 4
  ) +
  labs(
    title = "THg by Body Size in Hatchlings",
    x = expression(Log[10]~"SVL (cm)"),
    y = expression(Log[10]~"scute THg (" * mu * "g/g)")
  ) +
  theme_classic(base_size = 12)
```

# ------------------------------------------------------------
# Panel D: Hatchling vs juvenile THg
# ------------------------------------------------------------

```{r Figure-2-Panel-D}
pD <- ggplot(
  sizeclass_dat,
  aes(
    x = SizeClass,
    y = Hg_ugg,
    fill = SizeClass
  )
) +
  geom_boxplot(
    width = 0.55,
    alpha = 0.45,
    outlier.shape = NA,
    linewidth = 0.8
  ) +
  geom_jitter(
    aes(color = SizeClass),
    width = 0.12,
    height = 0,
    size = 2.5,
    alpha = 0.75
  ) +
  scale_fill_manual(values = age_colors) +
  scale_color_manual(values = age_colors) +
  
  # Descriptive juvenile:hatchling geometric mean ratio
  annotate(
    "text",
    x = 1.5,
    y = max(sizeclass_dat$Hg_ugg, na.rm = TRUE) * 1.08,
    label = paste0(
      sprintf("%.2f", fold_difference),
      "-fold higher\nin juveniles"
    ),
    size = 4.0
  ) +
  
  labs(
    title = "THg by Age Class",
    x = NULL,
    y = expression("Scute THg (" * mu * "g/g)")
  ) +
  
  guides(
    fill = "none",
    color = "none"
  ) +
  
  scale_y_continuous(
    expand = expansion(mult = c(0.05, 0.18))
  ) +
  
  theme_classic(base_size = 12) +
  
  theme(
    axis.text.x = element_text(
      face = "bold",
      color = "black"
    )
  )

```

# ------------------------------------------------------------
# Combine Figure 2 panels
# ------------------------------------------------------------

```{r assemble-Figure-2}
figure2 <- (
  pA + pB
) / (
  pC + pD
) +
  plot_annotation(
    tag_levels = "A",
    title = "Body Size and Age-Class Patterns in Scute Mercury Concentrations"
  ) &
  theme(
    plot.tag = element_text(
      face = "bold",
      size = 14
    ),
    plot.title = element_text(
      face = "bold"
    )
  )

figure2
```

# ============================================================
# FIGURE 3. HATCHLING CLUTCH AND NEST-SITE VARIATION
# ============================================================


# ------------------------------------------------------------
# Prepare hatchling plotting data
# ------------------------------------------------------------

```{r clutch-nest-site-variation}
hatchlings_plot <- hatchlings %>%
  mutate(
    Site_short = fct_recode(
      Site,
      "Playita" = "Isla Cabritos (Playita)",
      "Punte Oeste" = "Isla Cabritos (Punte Oeste)",
      "KM 5" = "KM 5",
      "Las Azufradas" = "Las Azufradas (La Charca)"
    ),
    
    Site_short = factor(
      Site_short,
      levels = c(
        "Playita",
        "Punte Oeste",
        "KM 5",
        "Las Azufradas"
      )
    ),
    
    Clutch_f = factor(
      Clutch_f,
      levels = c(
        "1", "3", "4", "5",
        "6", "7", "8", "9"
      )
    )
  )
```

# ------------------------------------------------------------
# Nest-site colors used only in Panel B
# ------------------------------------------------------------

```{r nest-site-colors}
site_colors <- c(
  "Playita" = "#0072B2",
  "Punte Oeste" = "#D55E00",
  "KM 5" = "#009E73",
  "Las Azufradas" = "#CC79A7"
)
```

# ------------------------------------------------------------
# Clutch-specific symbols used consistently in Panels A and B
# ------------------------------------------------------------

```{r clutch-specific-symbols}
clutch_shapes <- c(
  "1" = 16,
  "3" = 17,
  "4" = 15,
  "5" = 3,
  "6" = 4,
  "7" = 8,
  "8" = 18,
  "9" = 7
)
```

# ------------------------------------------------------------
# Unique clutch colors used only in Panel A
# Chosen to be distinct from the site palette in Panel B
# ------------------------------------------------------------

```{r clutch-colors}
clutch_colors <- c(
  "1" = "#332288",
  "3" = "#88CCEE",
  "4" = "#44AA99",
  "5" = "#117733",
  "6" = "#999933",
  "7" = "#DDCC77",
  "8" = "#AA4499",
  "9" = "#882255"
)
```

# ============================================================
# Panel A: Hatchling THg by clutch
# Color + shape both identify clutch
# ============================================================

```{r Figure-3-Panel-A}
p3A <- ggplot(
  hatchlings_plot,
  aes(
    x = Clutch_f,
    y = Hg_ugg,
    fill = Clutch_f,
    color = Clutch_f,
    shape = Clutch_f
  )
) +
  
  geom_boxplot(
    width = 0.60,
    alpha = 0.30,
    outlier.shape = NA,
    linewidth = 0.8
  ) +
  
  geom_jitter(
    width = 0.10,
    height = 0,
    size = 2.8,
    alpha = 0.85
  ) +
  
  scale_fill_manual(
    values = clutch_colors
  ) +
  
  scale_color_manual(
    values = clutch_colors
  ) +
  
  scale_shape_manual(
    values = clutch_shapes
  ) +
  
  annotate(
    "text",
    x = Inf,
    y = Inf,
    label = "ICC = 0.479",
    hjust = 1.10,
    vjust = 1.30,
    size = 4
  ) +
  
  labs(
    title = "Clutch-Level Variation",
    x = "Clutch",
    y = expression("Scute THg (" * mu * "g/g)")
  ) +
  
  guides(
    fill = "none",
    color = "none",
    shape = "none"
  ) +
  
  theme_classic(base_size = 12)
```

# ============================================================
# Panel B: Hatchling THg by nest site and clutch
# Color = nest site
# Shape = clutch
# ============================================================

```{r Figure-3-Panel-B}
p3B <- ggplot(
  hatchlings_plot,
  aes(
    x = Site_short,
    y = Hg_ugg,
    fill = Site_short
  )
) +
  
  geom_boxplot(
    width = 0.60,
    alpha = 0.35,
    outlier.shape = NA,
    linewidth = 0.8
  ) +
  
  geom_jitter(
    aes(
      color = Site_short,
      shape = Clutch_f
    ),
    width = 0.13,
    height = 0,
    size = 2.8,
    alpha = 0.90
  ) +
  
  scale_fill_manual(
    values = site_colors
  ) +
  
  scale_color_manual(
    values = site_colors
  ) +
  
  scale_shape_manual(
    values = clutch_shapes
  ) +
  
  annotate(
    "text",
    x = Inf,
    y = Inf,
    label = "Site: p = 0.151",
    hjust = 1.10,
    vjust = 1.30,
    size = 4
  ) +
  
  labs(
    title = "Nest Site and Clutch",
    x = "Nest site",
    y = expression("Scute THg (" * mu * "g/g)"),
    shape = "Clutch"
  ) +
  
  guides(
    fill = "none",
    color = "none",
    shape = guide_legend(
      title = "Clutch",
      override.aes = list(
        color = "black",
        size = 3.5,
        alpha = 1
      )
    )
  ) +
  
  theme_classic(base_size = 12) +
  
  theme(
    axis.text.x = element_text(
      angle = 25,
      hjust = 1
    )
  )

```

# ============================================================
# Combine Figure 3
# ============================================================

```{r assemble-Figure-3}
figure3 <- p3A + p3B +
  plot_annotation(
    tag_levels = "A",
    title = "Clutch and Nest-Site Variation in Hatchling Scute Mercury"
  ) &
  theme(
    plot.tag = element_text(
      face = "bold",
      size = 14
    ),
    plot.title = element_text(
      face = "bold"
    )
  )

figure3
```

# ============================================================
# 7. SAVE OUTPUTS
# ============================================================

```{r save-outputs}
write.csv(
  clutch_structure,
  "Hatchling_Clutch_Structure.csv",
  row.names = FALSE
)

write.csv(
  site_results,
  "Nest_Site_Estimated_Hg.csv",
  row.names = FALSE
)

write.csv(
  juvenile_sex_summary,
  "Juvenile_Sex_Summary.csv",
  row.names = FALSE
)

write.csv(
  sex_results,
  "Juvenile_Sex_Adjusted_Hg.csv",
  row.names = FALSE
)

write.csv(
  sizeclass_summary,
  "SizeClass_Hg_Summary.csv",
  row.names = FALSE
)

write.csv(
  sizeclass_geo,
  "SizeClass_Geometric_Means.csv",
  row.names = FALSE
)
```

# ------------------------------------------------------------
# Save CV sensitivity-analysis outputs
# ------------------------------------------------------------

```{r sensitivity-analysis-outputs}
write.csv(
  dat %>%
    select(
      `Scute ID`, SizeClass, Sex, Clutch, Site,
      n_subsamples, Hg_ugg, SD_Hg_ugg,
      CV_percent, CV15_status, CV15_include
    ),
  "Scute_Subsample_CV_by_Individual.csv",
  row.names = FALSE
)

write.csv(
  CV15_sample_summary,
  "CV15_Sample_Summary.csv",
  row.names = FALSE
)

write.csv(
  CV15_excluded_individuals,
  "CV15_Excluded_Individuals.csv",
  row.names = FALSE
)

write.csv(
  CV15_n_comparison,
  "CV15_Primary_vs_Sensitivity_Sample_Sizes.csv",
  row.names = FALSE
)

write.csv(
  CV15_model_summary,
  "CV15_Primary_vs_Sensitivity_Model_Summary.csv",
  row.names = FALSE
)
```

# ------------------------------------------------------------
# Save Figure 2
# ------------------------------------------------------------

```{r save-Figure-2}
ggsave(
  "Figure2_BodySize_SizeClass.tiff",
  figure2,
  width = 11,
  height = 8,
  units = "in",
  dpi = 600,
  compression = "lzw"
)
```

## ------------------------------------------------------------
## Save Figure 3
## ------------------------------------------------------------

```{r save-Figure-3}
ggsave(
  "Figure3_Clutch_NestSite.tiff",
  figure3,
  width = 10,
  height = 5,
  units = "in",
  dpi = 600,
  compression = "lzw"
)
```

```{r manifest}
rsconnect::writeManifest(
  appDir = here(),
  appPrimaryDoc = "American_Crocodile_Hg_Analyses.Rmd"
)
```



